High geomagnetic field intensity recorded by anorthosite xenoliths requires a vigorous late Mesoproterozoic geodynamo

### 2022-01-28 PNAS_manuscript/Supporting Info.tex
Updates from Overleaf

% \begin{figure*}[h!]
% \noindent\includegraphics[width=17.8 cm]{manuscript/nonlinear.pdf}
% \centering
% \caption{{}}
% \label{fig:nonlinear_check}
% \end{figure*}

>>>>

\begin{figure*}[h!]
\noindent\includegraphics[width=0.9\textwidth]{Linear_TRM_test.pdf}
\centering
\caption{{Plot of linear thermal remanent magnetization acquisition experiments. After IZZI-type Thellier paleointensity experiments, full TRMs were imparted on the same specimens in known lab fields of 30, 50, 70, and 90 $\mu$T. The results show that the anorthosite xenoliths do not acquire saturation remanence or display non-linear remanence acquisition under fields relevant to this study. Therefore, non-linear acquisition correction is not needed for our paleointensity results. }}
\label{fig:nonlinear_check}
\end{figure*}
